QPLIB: A Library of Quadratic Programming Instances

### 2017-01-29 QPLIB-3.tex
add sparsity pattern for one instance

The instances of QPLIB are publicly accessible at the website \url{http://qplib.zib.de}.
%
Beyond all instances in GAMS and \texttt{.lp} format, the website provides a rich set of metadata for each
instance: the three letter problem classification (as described in Section \ref{subsec:final set}), basic properties such as the number of variables and constraints of
different types, the sense and convexity/concavity of the objective function, and information on the nonzero structure of the
problem.
%
In addition, we display a visualization of the sparsity patterns of the Jacobian and the Hessian matrix of the
Lagrangian function.  In the plots of the Jacobian nonzero pattern, the linear and nonlinear entries are distinguished
by color.  Figure... shows an example for instance QPLIB... \todo{add figure}

>>>>

The instances of QPLIB are publicly accessible at the website \url{http://qplib.zib.de}.
Scripts and tools developed for MINLPLib 2 \cite{Vigerske2014} were used and extended to create the website.
%
Beyond all instances in GAMS and \texttt{.lp} format, the website provides a rich set of metadata for each
instance: the three letter problem classification (as described in Section \ref{subsec:final set}), basic properties such as the number of variables and constraints of
different types, the sense and convexity/concavity of the objective function, and information on the nonzero structure of the
problem.
%
In addition, we display a visualization of the sparsity patterns of the Jacobian and the Hessian matrix of the
Lagrangian function.  In the plots of the Jacobian nonzero pattern, the linear and nonlinear entries are distinguished
by color.  Figure \ref{fig:sparsitypattern} shows an example for instance QPLIB\_2967.

\begin{figure}
\centering
\includegraphics[scale=0.5]{{QPLIB_2967.jac}.png} \qquad
\includegraphics{{QPLIB_2967.hess}.png}
\caption{Sparsity pattern of Gradient of objective (first line) and Jacobian (left) and of Hessian of Lagrangian function (right) for instance QPLIB\_2967.}
\label{fig:sparsitypattern}
\end{figure}
